Robust Control of a Fluxonium Qubit

### 2020-09-30 paper/main.tex

  \caption{
    (a) X/2 gates robust to qubit frequency detunings constructed using the
    analytic, 2-point sampling, 8-point unscented sampling, and (2\textsuperscript{nd},
    3\textsuperscript{rd})-order derivative methods at a gate duration of $56.8$ns.
    (b) Single gate error as
    a function of the gate duration at a one-percent
    detuning from the nominal qubit frequency for all methods.
    (c) Single gate error as a function of the detuning from the nominal
    qubit frequency at gate durations of $56.8$ns and $120$ns for the analytic
    and 2\textsuperscript{nd}-order derivative methods.
  }
\end{figure*}

>>>>

  \caption{
    (a) Z/2 gates constructed using the
    analytic, 2-point sampling, 8-point unscented sampling, and the 1\textsuperscript{st}
    and 2\textsuperscript{nd} order derivative methods. The gates
    shown for the robust methods are the solutions at twice the analytic
    gate time.
    (b) Single gate error as
    a function of the gate duration at a one-percent
    detuning from the nominal qubit frequency for all methods.
    (c) Single gate error as a function of the detuning from the nominal
    qubit frequency at multiples of the analytic gate duration for the analytic
    and 1\textsuperscript{st} order derivative methods.
  }
\end{figure*}
